---
title: "data"
author: "MarenaO"
date: '2022-03-28'
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
require(tigerstats)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")

favstats(my1000)
```

The resulting plot shows two peaks, making it bimodal. The peaks have bimodal distribution, meaning that there are two values in the data that have the highest frequencies rather than one. One of the peaks seems to be slighlty shorter than the other one, but for the most part, they appear to be the same size.

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")

favstats(x.avg)
```

The resulting plot has three peaks, meaning it is trimodal. The peaks have trimodal distribution. The middle peak was twice as high as the ones on the end. The peaks on the end were half as short. The left peak represents the low-low values, which happen a quarter of the time, and the right peak represents the high-high values, which happen a quarter of the time. The peak in the middle represents the low-high, high-low, which happens half of the time.

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")

favstats(x.avg)
```

The resulting plot for sample 4 looks like it has 5 peaks. The peak in the center is the tallest, the peaks on the side of the center peak are the second tallest, and the peaks at the edge of the second tallest peaks are the shortest. According to the CLT, the standard deviation should drop to half the original size. In this case it did. The standard deviation of the original sample size was 41.67. In this sample size 4, the standard deviation dropped to about half of 41.67, which was 20.7.

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")

favstats(x.avg)
```

The resulting plot for sample size 9 attempts to act like a normal distribution curve, although it is not quite one. It has some small peaks near the top of the plot. According to the CLT, the standard deviation should drop to a third of the original value for sample 9. In this case it did. The original value of 41.67 dropped to a value of 13.79 in sample 9.
```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")

favstats(x.avg)
```

The resulting plot of sample 16 also attempts to act like a normal distribution curve, although, again it is not quite there. There are a couple smaller peaks near the top of the plot. According to the CLT, the standard deviation in sample 16 should drop down to a quarter of its original size. In this case it did. The original standard deviation was 41.67, and in sample 16 it dropped down to 10.33, which is about a quarter of its original size.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")

favstats(x.avg)
```

According to the central limit theorem
